Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-07-02 man/figures/resilience_long_term.Rmd
update

**Figure 6.** Resilience metrics of the tree-growth for the most severe drought events (as from Table S3). *Left*: Resistance (*Rt*); *Center*: Recovery (*Rc*); *Right*: Resilience (*Rs*). Points indicate average of resilience metrics for all populations. Error bar corresponds standard error. Resilience metrics were computed for each population (sample depth > 10) and drought event.

@@

```{r, eval=FALSE, echo=FALSE}
dff <- sdf %>% 
  dplyr::select(d_severity, rt_mean_mean, rs_mean_mean, rc_mean_mean) %>% 
  gather(key = res_metric, value,c(rt_mean_mean,rs_mean_mean,rc_mean_mean))

@@

plotrelsite <- function(df, v, x, label, site, titulo, coord_eqX, ...){
  require(ggplot2)
  require(ggrepel)
  require(purrr)

@@

  ggplot(df, 
         aes_string(y=paste0(v, "_mean_mean"), x=x, label=label, colour=site, fill=site)) +
    geom_smooth(method='lm', se=FALSE, aes(group=1), colour='gray',  size = 1) + # linetype = "dotted",
    geom_smooth(method='lm', se=FALSE) + 
    geom_point(size=1.5, pch = 21) + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 2, show.legend = FALSE) + 
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10)) +
    geom_text_repel(data = eqns, aes(x = coord_eqX, y = Inf, label = equation),
                    direction = "y", segment.size = 0, hjust = 0,
                    parse = TRUE, show.legend = FALSE)
}

@@

sevRt_site <- plotrelsite(sdfsite, v = "rt", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rt", coord_eqX = Inf) + xlab('') + ylab('') + xlim(5,25)

>>>>

@@

**Figure 6.** Resilience metrics of the tree-growth for severe drought events since 1950. *Left*: Resistance (*Rt*); *Center*: Recovery (*Rc*); *Right*: Resilience (*Rs*). Points indicate resilience metrics for oak populations: SJ (*blue*), CA-High (*red*) and CA-Low (*green*). Resilience metrics were computed for each population (sample depth > 10) and drought event. Gray line represents overall relationship for each Resilience metrics.

```{r, echo=FALSE}
dff <- sdf %>% 
  dplyr::select(d_severity, rt_mean_mean, rs_mean_mean, rc_mean_mean) %>% 
  gather(key = res_metric, value,c(rt_mean_mean,rs_mean_mean,rc_mean_mean))

@@

plotrelsite <- function(df, v, x, label, site, titulo, coord_eqX, xLM, yLM, ...){
  require(ggplot2)
  require(ggrepel)
  require(purrr)

@@

  ggplot(df, 
         aes_string(y=paste0(v, "_mean_mean"), x=x, label=label, colour=site, fill=site)) +
    geom_smooth(method='lm', se=FALSE, aes(group=1), colour='gray',  size = 1) + # linetype = "dotted",
    geom_smooth(method='lm', se=FALSE) + 
    geom_point(size=1.5, pch = 21) + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 2, show.legend = FALSE) + 
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10)) +
    geom_text_repel(data = eqns, aes(x = coord_eqX, y = Inf, label = equation),
                    direction = "y", segment.size = 0, hjust = 0,
                    parse = TRUE, show.legend = FALSE) +
    annotate("text", x = .0, y = 10, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE, 
             size = 5, fontface = "bold", hjust="left") 
}

@@

sevRt_site <- plotrelsite(sdfsite, v = "rt", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rt", coord_eqX = Inf) + xlab('') + ylab('')

+ 
  xlim(5,25)
